Finiteness in Cubical Type Theory

### 2020-07-02 sections/search.tex
changed agda code a bit

The proof that this type is finite mirrors its definition closely:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{expr-finite}
\end{agdalisting}
\subsection{Filtering to Correct Expressions}
\section{Automating Proofs}

>>>>

The proof that this type is finite mirrors its definition closely:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{expr-finite}
\end{agdalisting}
\subsection{Filtering to Correct Expressions}
We now have a way to construct, formally, every expression we can generate from
a given list of numbers.
This is incomplete in two ways, however.
Firstly, some expressions are invalid: we should not, for instance, be able to
divide two numbers which do not divide evenly.
Secondly, we are only interested in those expressions which actually represent
solutions: those which evaluate to the target, in other words.
We can write a function which tells us if both of these things hold for a given
expression like so:
\begin{multicols}{2}
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{eval}
  \end{agdalisting} \columnbreak
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{app-op}
  \end{agdalisting}
\end{multicols}
\section{Automating Proofs}
